\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
2nd September 2014 \\
\medskip
Ericsson\\
\medskip
Re: Junior Software Developer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I decided to enter the engineering profession because I firmly believe the most positive way to impact our world is to build.
This is because I am a firm believer that the surest way to positively impact our world is the creation of new technologies.
One of the greatest things technology has done is bring us closer and make us more connected.
What keeps increasing this world's inter-connectivity is the work of firms like yours, and the work of corporations like your push us further into the future. 
I believe that my 
programming and scripting skills and
experience developing for embedded systems
make me a good fit for this position.\\
\medskip
\hspace{10mm}
%Proficiency in C/C++ development for embedded systems;
During my first co-op work term at UBC, I was tasked with the development of a mini-MRI control system using an Arduino, which communicated with a PC.
The Arduino program was coded in C++, and the PC ran a program written in Python. The Python program had a GUI component, processed data collected by the 
micro-controller, and graphed it on the PC's monitor as the data streamed in.
%Proficiency in using compilers, linkers, emulators, debugging tools and revision control tools;
Throughout my coding experience, I have had to use different methods of compiling an executable program. 
In my schoolwork, I used Visual Studio; during my work at UBC, I used GNU Make and during my work at Epic 3D, I used CMake.
I've also used Git for version control.
%Experience with scripting languages such as Python or Ruby
%Hardware design and debug experience
I've also been tasked with circuit design and testing, using tools like oscilloscopes to analyse waveforms and debug the circuit.
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
I am proactive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}