\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
19th August 2014 \\
\medskip
MineSense Technologies Ltd\\
\medskip
Re: Junior Software Developer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I decided to enter the engineering profession because I firmly believe the most positive way to impact our world is to build.
The efforts of companies such as your own are exemplary of the kind of work needed to keep improving our qualities of life.
I believe that my programming and scripting skills, experience developing for embedded systems, and knowledge of software development for 
microcontrollers make me a good fit for this position.
\\
\medskip
\hspace{10mm}
All development involved the process of planning, analysis of behaviour, troubleshooting, debugging, and iteration.
During my co-op term at UBC, I was tasked with the development of the code controlling a mini-MRI machine, which was written in C, C++ and Python.
During my work term at Honda Research Institute, the head tracking program I was tasked with was written in C++.
In all cases, the code I wrote was built to be modular for reusability, and commentated for easy modification by my successors.
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
I am proavtive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.
\\

\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}