\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
8th August 2014 \\
\medskip
MDA Corporation\\
\medskip
Re: New Graduate Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I began my university education with the intention of working in the field of research and development. This is because I am a firm believer that the 
surest way to positively impact our world is the creation of new technologies. Your corporation's work on the Canadarm is a shining example of the type
of work that needs to be done to bring us into the world of tomorrow. I believe that my programming and scripting skills, experience developing 
functional systems, and knowledge MATLAB, image processing, and GUI development make me a good fit for this position.\\
\medskip
\hspace{10mm}
During my co-op position at UBC, I was tasked with the development of the code controlling a mini-MRI machine, which was written in C, C++ and Python.
The work involved creating a GUI using PyGTK, which is an open-source toolkit. The position also required work to be done in Gentoo, a Linux-based OS. 
During my work term at Honda Research Institute, one task I completed was the detection of an object's position in space, which I achieved by applying
a spherical marker and using OpenCV to process the input image.
Another task I was assigned at Honda was the processing of data collected, which was done in MATLAB.\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
I am proactive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}