\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
19th August 2014 \\
\medskip
PMC Sierra\\
\medskip
Re: Product Verification Engineer position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I began my university education with the intention of working in the field of research and development. This is because I am a firm believer that the 
surest way to positively impact our world is the creation of new technologies. I believe that my programming and scripting skills, experience 
using Modelsim, and knowledge of VHDL make me a good fit for this position.
\\
\medskip
\hspace{10mm}
While developing the VHDL modules for my final year project and other projects involving the DE II, all modules are tested using Modelsim. For each 
module, a testbench is written, and the waveform is inspected to ensure that the behaviour is as per design. 
When the behaviour varied from expectation, the code was debugged and retested.
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
I am proavtive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
\\
\medskip
\hspace{10mm}
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}