\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
13th August 2014 \\
\medskip
Sierra Wireless\\
\medskip
Re: Junior Firmware Engineer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I began my university education with the intention of working in the field of research and development. 
This is because I am a firm believer that the surest way to positively impact our world is the creation of new technologies. 
What keeps increasing this world's interconnectivity is the work of firms like yours, and the work of corporations like your push us into the future. 
I believe that my programming and scripting skills, experience developing for embedded systems, and knowledge of microcontrollers 
make me a good fit for this position.\\
\medskip
\hspace{10mm}
During my co-op position at UBC, I was tasked with the development of the code controlling a mini-MRI machine, which was controlled by an Arduino
microcontroller, coded using the Arduino's own IDE using C/C++. I was again tasked with use of the Arduino during my work term with Epic 3D Tech,
where it was used to control an automated 3D camera rig with stepper motors.
In both these cases, it was required for the microcontroller to communicate with an external device, whether through the 2 pin UART to a Bluetooth
transmitter/receiver or the USB pseudo-UART to a PC.
All development involved the process of planning, analysis of behaviour, troubleshooting, debugging, and iteration. 
In addition, each functional iteration was commited to a GIT repository for both accessibility from the network and backing up previous work for roll-backs.
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
I am proactive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}