\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
29th September 2014 \\
\medskip
HydroRun Technologies Ltd.\\
\medskip
Re: Electronics/Firmware Design Engineer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I decided to enter the engineering profession because I firmly believe the most positive way to impact our world is to build.
I began my university education with the intention of working in the field of research and development. 
This is because I am a firm believer that the surest way to positively impact our world is the creation of new technologies.
The generation of electric power is one of the largest challenges we face today, and the work done by firms like yours is paramount to the continued
prosperity of all.
I believe that my embedded systems programming skills and experience learning new technologies make me a good fit for this position.
\\
\medskip
\hspace{10mm}
%Embedded systems programming
%Experience developing mission-critical real-time firmware
During my first co-op work term at UBC, I was tasked with the development of a mini-MRI control system using an Arduino, which communicated with a PC.
The Arduino program was coded in C++, and it contained a list of possible actions to take with variables associated with duration and specific function.
It then awaited a list of instructions to execute from the client PC, or an execution command.
%Experience designing and building instrumentation
In my capstone project, I designed the circuitry needed to capture the signal put out by the scanning electron microscope column as well as control it
using an array of A/D and D/A converters. 
%Experience working with new technology
In all my co-op positions I have been required to learn and utilise new hardware and software, such as new programming languages, operating systems,
and hardware components.
\\
\medskip
\hspace{10mm}
%Curious, takes initiative, and self directed
%Excellent written and oral communication skills
As an individual I have had a track record of being enthusiastic while being even keeled. 
I am proavtive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}