\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
22nd August 2014 \\
\medskip
SemiosBIO Technologies Inc.\\
\medskip
Re: Embedded Software Engineer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I decided to enter the engineering profession because I firmly believe the most positive way to impact our world is to build.
This is because I am a firm believer that the surest way to positively impact our world is the creation of new technologies.
Innovatation, like the kind of work your company does, is what pushes us into the world of tomorrow.
I believe that my experience developing for embedded systems and reading circuit schematics make me a good fit for this position.
\\
\medskip
\hspace{10mm}
%Minimum one year of embedded software engineering development experience
At my co-op position with UBC, I used the Arduino micro-controller and various Python modules to build a system to control a mini-MRI machine.
At my next position with Epic 3D Tech, I was tasked with use of the Arduino during my work term with Epic 3D Tech, where it was used to control an automated 3D camera rig with stepper motors.
%A minimum of 6 months of circuit design and reading of schematics
In my final year project, the first step was to peruse the schematics of the existing scanning electron microscope to determine the 
inputs required for operation.
%Circuit design, board layout and prototype
Once the required waveforms were determined, the next step was designing circuits to generate the waveform.
%Adequate knowledge of reading schematics and data sheets for components
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
I am proactive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.
\\
\medskip
\hspace{10mm}
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}