\documentclass[10pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
13th August 2014 \\
\medskip
Honeywell\\
\medskip
Re: Electronics Engineer II Position (Job Number: 00244244)\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I began my university education with the intention of working in the field of research and development. This is because I am a firm believer that the 
surest way to positively impact our world is the creation of new technologies.
The ubiquity of your company's products, as well as the breadth of the products it develops leads me to believe that your company is a great
place to learn and gain experience. 
I believe that my programming and scripting skills, experience circuit prototyping, and knowledge of software development for microcontrollers 
make me a good fit for this position.\\
\medskip
\hspace{10mm}
In my final year project, my team and I developed an Altera DE2 board-based solution for the control system for a scanning electron microscope,
which communicated to a host PC via RS-232, and a Nios II soft processor programmed in C was used to handle communication.
%• Programming (C, C++) of microcontrollers (PIC, LonWorks, FPGAs), multi-platform adaptability, high and low level programming, drivers, etc.
During my work term with Epic 3D Tech, I was tasked with the control of an automated 3D camera rig, where the rig was manipulated by four stepper motors.
This was achieved by powering the motors with a H-bridge circuit, and having a tracked position with a calibrating microswitch and 
programatically tracked with an Arduino microcontroller.
%• Electronic, analog / digital circuit design, test and troubleshooting. 
%• Previous experience designing electronics for stepper motor control and positioning
Throughout both my time at university and working at my various co-op positions, I have had to do quick prototyping using breadboards and 
breakout boards to test the behaviour of the circuitry.
%• Proficiency with rapid design and rapid prototyping: bare board manufacturing, building, testing and assembling various design concepts.
\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
As an engineering student, I have been subject to many short-term as well as term-length projects.
In many of these projects, I have had to present the results of the project before my peers and instructors.
I am proactive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.
I look forward to further discussing my qualifications with you in person.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}