\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\flushleft
\large
421-2960 Princess Crescent,\\
Coquitlam, BC V3B 7P2 \\
\medskip
8th August 2014 \\
\medskip
PMC Sierra\\
\medskip
Re: Product Engineer Position\\
\medskip
Dear Sir/Madam,\\

\medskip
\hspace{10mm}
I began my university education with the intention of working in the field of research and development. This is because I am a firm believer that the 
surest way to positively impact our world is the creation of new technologies. I believe that my programming and scripting skills, experience 
developing functional systems, and knowledge of semiconductor and RF fundamentals make me a good fit for this position.\\
\medskip
\hspace{10mm}
In all my co-op positions I have been required to learn and utilise new hardware and software. For instance, at my first co-op position, I learned to
to use the Arduino micro-controller, the Linux operating system and various Python modules simultaneously. At Epic 3D Tech, I have been tasked with 
the development of control modules. The development involved the process of planning, analysis of behaviour, troubleshooting, debugging, and iteration. 
I have also taken a university course pertaining to RF antennae and propagation, giving me the knowledge of the RF fundamentals.\\
\medskip
\hspace{10mm}
As an individual I have had a track record of being enthusiastic while being even keeled. 
I am proavtive in bridging gaps in my knowledge and skills, and am motivated by learning new things.
Through the course of my time as a student, I have had to write many essays, proposals, reports and memoranda, giving me a deal of experience in writing.
Thank you for taking the time to read this cover letter.\\


\bigskip
Regards, \\
Daniel Hon Kit Chong
\end{document}